Manuscript1_figures

### 2025-09-10 Manuscript1_figures.Rmd
Created extra DO plot to show how HOx increases DO

@@

>>>>

DOF4 <- DO4 %>% 
  filter(Reservoir == 'FCR')

@@

```{r}
DO_plot2 <- DO %>%
  filter(Reservoir == 'FCR') %>% 
  ggplot() + theme_bw() + theme(panel.grid = element_blank()) + 
  facet_grid(cols = vars(Year), scales = 'free') +
  scale_x_date(date_labels = '%b', breaks = '3 months') +
  geom_line(aes(x = Date, y = DO_mgL, color = Reservoir)) +
  geom_point(aes(x = Date, y = DO_mgL, color = Reservoir),
             data = DOF4, size = 0.5) +
  geom_rect(aes(xmin = HOxOn, xmax = HOxOff, group = Group), ymin = -Inf, ymax = Inf, data = HOxBoxes, alpha = 0.2) +
  ylab('Dissolved Oxygen (mg/L)')

```
